# 简介 {#intro}

```{r, echo = FALSE}
source("common.R")
```

```{r, include = FALSE, eval = FALSE}
# takes a few seconds
x <- tools::CRAN_package_db()
nrow(x)
```

在 R 中，软件包是可共享代码的基本单位。
软件包将代码、数据、文档和测试整合到一起，使其很容易与别人分享。
截止到 2022 年 6 月，在综合 R 档案网络 (**C**omprehensive **R** **A**rchive **N**etwork)，或者说 R 包的公共信息交换平台 CRAN 上已经有 18,000 多个可用的软件包。
这些种类繁多的软件包是 R 语言如此成功的原因之一：很可能已经有人已经解决了你正在研究的问题，因此你可以通过下载他们的软件包来从中获益。

如果你正在读这本书，那么就应该已经知道如何通过以下方式来使用软件包了：

-   从 CRAN 中下载安装：`install.packages("x")`。
-   在 R 中使用： `library("x")` 或 `library(x)。
-   获取帮助信息：`package?x` 或 `help(package = "x")`。

本书的目标是教你如何开发软件包，以便你能编写自己的软件包，而不仅仅是使用别人的软件包。
那么为什么要开发软件包呢？
一个很强烈的理由是，你有想要与别人分享的代码。
把你的代码整合进一个软件包里后，其他人能够很容易地使用，因为和你一样，他们也知道如何使用包。
因此如果你的代码整合进了一个软件包中，任何 R 语言的用户都可以很容易地下载、安装并学习如何使用它。

但即使你不共享代码，软件包依然很有用。
正如 Hilary Parker 在 [introduction to packages](https://hilaryparker.com/2014/04/29/writing-an-r-package-from-scratch/) 中所说的: "Seriously, it doesn't have to be about sharing your code (although that is an added benefit!). It is about saving yourself time."， 将代码组织在软件包中可以让工作生活更加轻松，因为软件包遵循一些通用的约定。
例如，你需要将 R 代码文件放在 `R/` 目录下，将测试文件放在 `tests/` 目录下，还有将数据文件放在 `data/` 目录下。
这些约定很有用，因为：

-   它们能节省时间——你不需要考虑如何组织软件包才是最佳的，只需要按照模板操作就好。

-   标准化的规范带来标准化的工具——如果你遵循 R 软件包的封装规范，就能够免费获得许多工具。

你的数据分析流程甚至也可以用软件包来构建（例如 @marwick2018-tas 或 @marwick2018-peerj），不过我们不会在这里深入研究这个用例。

## Philosophy {#intro-phil}

This book espouses our philosophy of package development: anything that can be automated, should be automated.
Do as little as possible by hand.
Do as much as possible with functions.
The goal is to spend your time thinking about what you want your package to do rather than thinking about the minutiae of package structure.

This philosophy is realized primarily through the devtools package, which is the public face for a suite of R functions that automate common development tasks.
The release of version 2.0.0 in October 2018 marked its internal restructuring into a set of more focused packages, with devtools becoming more of a meta-package.
The usethis package is the sub-package you are most likely to interact with directly; we explain the devtools-usethis relationship in @sec-setup-usage.

As always, the goal of devtools is to make package development as painless as possible.
It encapsulates the best practices developed by Hadley Wickham, initially from his years as a prolific solo developer.
More recently, he has assembled a team of developers at RStudio, who collectively look after hundreds of open source R packages, including those known as [the tidyverse](https://www.tidyverse.org).
The reach of this team allows us to explore the space of all possible mistakes at an extraordinary scale.
Fortunately, it also affords us the opportunity to reflect on both the successes and failures, in the company of expert and sympathetic colleagues.
We try to develop practices that make life more enjoyable for both the maintainer and users of a package.
The devtools meta-package is where these lessons are made concrete.

devtools works hand-in-hand with RStudio, which we believe is the best development environment for most R users.
The main alternative is [Emacs Speaks Statistics](https://ess.r-project.org/) (ESS), which is a rewarding environment if you're willing to put in the time to learn Emacs and customise it to your needs.
The history of ESS stretches back over 20 years (predating R!), but it's still actively developed and many of the workflows described in this book are also available there.
For those loyal to vim, we recommend the [Nvim-R plugin](https://github.com/jalvesaq/Nvim-R).

::: callout-tip
## RStudio

Throughout the book, we highlight specific ways that RStudio can expedite your package development workflow, in specially formatted sections like this.
:::

Together, devtools and RStudio insulate you from the low-level details of how packages are built.
As you start to develop more packages, we highly recommend that you learn more about those details.
The best resource for the official details of package development is always the official [writing R extensions](https://cran.r-project.org/doc/manuals/R-exts.html#Creating-R-packages) manual[^introduction-1].
However, this manual can be hard to understand if you're not already familiar with the basics of packages.
It's also exhaustive, covering every possible package component, rather than focusing on the most common and useful components, as this book does.
Writing R extensions is a useful resource once you've mastered the basics and want to learn what's going on under the hood.

[^introduction-1]: You might also enjoy the "quarto-ized" version at [https://rstudio.github.io/r-manuals/r-exts/](https://rstudio.github.io/r-manuals/r-exts/Function-and-variable-index.html).

## In this book {#intro-outline}

<!-- TODO: proof read this section -->

The first part of the book is all about giving you all the tools you need to start your package development journey and we highly recommend that you read it in order.
We begin in @sec-whole-game with a run through the complete development of a small package.
It's meant to paint the big picture and suggest a workflow, before we descend into the detailed treatment of the key components of an R package.
Then in @sec-setup you'll learn how to prepare your system for package development, and in @sec-package-structure-state you'll learn the basic structure of a package and how that varies across different states.
Next, in @sec-workflows101, we'll cover the core workflows that come up repeatedly for package developers.
Then the first section of the book in @sec-package-within with another case study, this time focusing on how you might convert a script to a package and discussing the challenges you'll face along the way.

The remainder of the book is design to be read as needed.
Pick and choose between the chapters as you need them.

First we cover key package components: @sec-r discusses where your code lives and how to organize it, @sec-data shows you how to include data in your package, and @sec-misc covers a few less important files and directories that need to be discussed somewhere.

Next we'll dive into to the package metadata, starting with `DESCRIPTION` and `NAMESPACE` in @sec-metadata.
We'll then go deep into dependencies in @sec-dependencies, discussing when and how to depend on another package.
We'll finish off this part with a look at licensing in @sec-license.

To ensure your package works as designed (and continues to work as you make changes), it's essential to test your code, so the next three chapters cover the art and science of testing.
@sec-testing-basics gets you started with the basics of testing with the testthat package.
@sec-testing-design teaches you how to design and organise tests in the most effective way.
Then we finish off our coverage of testing in @sec-testing-advanced which teaches you advanced skills to tackle the most challenging of cases.

If you want other people (including future-you!) to understand how to use the functions in your package, you'll need to document them.
@sec-man gets you started using roxygen to document the functions in your package.
Function documentation is only helpful if you know what function to look up, so next in @sec-vignettes we'll discuss vignettes, which help you document the package as a whole.
We'll finish up documentation with a discussion of other important markdown files like `README.md` and `NEWS.md` in @sec-man-markdown, and creating a package website with pkgdown in @sec-website.

The book concludes with a look at the release of your package to CRAN and the maintenance thereafter.
@sec-r-cmd-check dives into `R CMD check`, the most important tool for verifying your package is free from major defects.
You'll then learn how you can run `R CMD check` automatically every time you change your package in @sec-ci.
If you're planning on submitting your package to CRAN, @sec-release shows you the process and gives you our tips and tricks to maximize the chances of success.
We conclude with a discussion the post-release lifecycle in @sec-lifecycle.

This is a lot to learn, but don't feel overwhelmed.
Start with a minimal subset of useful features (e.g. just an `R/` directory!) and build up over time.
To paraphrase the Zen monk Shunryu Suzuki: "Each package is perfect the way it is --- and it can use a little improvement".

## What you won't learn {#you-wont-learn}

There are a few very important topics that you won't learn about in this book:

<!-- TODO: complete these comments -->

-   Git and GitHub: mastering a version control system is vital to easily collaborate with others, and is useful even for solo work because it allows you to easily undo mistakes.
    Learn from <https://happygitwithr.com/>.

-   Compiled code: R code is designed for human efficiency, not computer efficiency, so it's useful to have a tool in your back pocket that allows you to write fast code.
    Learn more in <https://adv-r.hadley.nz/rcpp.html>, or <https://cpp11.r-lib.org>.

-   Markdown and RMarkdown.

There are also specific practices that have little to no treatment here simply because we do not use them enough to have any special insight.
Does this mean that we actively discourage those practices?
Probably not, as we try to be explicit about practices we think you should avoid.
So if something is not covered here, it just means that a couple hundred heavily-used R packages are built without meaningful reliance on that technique.
That observation should motivate you to evaluate how likely it is that your development requirements truly don't overlap with ours.
But sometimes the answer is a clear "yes", in which case you'll simply need to consult another resource.

## Acknowledgments {#intro-ack}

```{r eval = FALSE, include = FALSE}
# code generates fodder for the prose below
library(desc)

get_contributors <- function(pkg = "devtools") {
  desc_get_authors(system.file("DESCRIPTION", package = pkg))
}
# using packages represented by hex stickers in 2019 usethis useR! talk
# team agreed that was the "right" set of packages
get_contributors("devtools")
get_contributors("usethis")
get_contributors("testthat")
get_contributors("pkgload")

get_contributors("rcmdcheck")
get_contributors("sessioninfo")
get_contributors("remotes")
get_contributors("revdepcheck")

get_contributors("pkgbuild")
get_contributors("roxygen2")
get_contributors("desc")
get_contributors("withr")
```

Since the first edition of R Packages was published, the packages supporting the workflows described here have undergone extensive development.
The original trio of devtools, roxygen2, and testthat has expanded to include the packages created by the "conscious uncoupling" of devtools, as described in @sec-setup-usage.
Most of these packages originate with Hadley Wickham (HW), because of their devtools roots.
There are many other significant contributors, many of whom now serve as maintainers:

-   devtools: HW, [Winston Chang](https://github.com/wch), [Jim Hester](https://github.com/jimhester) (maintainer, \>= v1.13.5)
-   usethis: HW, [Jennifer Bryan](https://github.com/jennybc) (maintainer \>= v1.5.0)
-   roxygen2: HW (maintainer), [Peter Danenburg](https://github.com/klutometis), [Manuel Eugster](https://github.com/mjaeugster)
-   testthat: HW (maintainer)
-   desc: [Gábor Csárdi](https://github.com/gaborcsardi) (maintainer), [Kirill Müller](https://github.com/krlmlr), [Jim Hester](https://github.com/jimhester)
-   pkgbuild: HW, [Jim Hester](https://github.com/jimhester) (maintainer)
-   pkgload: HW, [Jim Hester](https://github.com/jimhester) (maintainer), [Winston Chang](https://github.com/wch)
-   rcmdcheck: [Gábor Csárdi](https://github.com/gaborcsardi) (maintainer)
-   remotes: HW, [Jim Hester](https://github.com/jimhester) (maintainer), [Gábor Csárdi](https://github.com/gaborcsardi), [Winston Chang](https://github.com/wch), [Martin Morgan](https://github.com/mtmorgan), [Dan Tenenbaum](https://github.com/dtenenba)
-   revdepcheck: HW, [Gábor Csárdi](https://github.com/gaborcsardi) (maintainer)
-   sessioninfo: HW, [Gábor Csárdi](https://github.com/gaborcsardi) (maintainer), [Winston Chang](https://github.com/wch), [Robert Flight](https://github.com/rmflight), [Kirill Müller](https://github.com/krlmlr), [Jim Hester](https://github.com/jimhester)

This book and the R package development community benefit tremendously from experts who smooth over specific pain points:

-   [Kevin Ushey](https://github.com/kevinushey), [JJ Allaire](https://github.com/jjallaire), and [Dirk Eddelbuettel](http://dirk.eddelbuettel.com) tirelessly answered all sorts of C, C++, and Rcpp questions.
-   [Craig Citro](https://github.com/craigcitro) wrote much of the initial code to facilitate using Travis-CI with R packages.
-   [Jeroen Ooms](https://github.com/jeroen) also helps to maintain R community infrastructure, such as the current R support for Travis-CI (along with Jim Hester), and the Windows toolchain.

*TODO: revisit rest of this section when 2nd edition nears completion. Currently applies to and worded for 1st edition.*

Often the only way I learn how to do it the right way is by doing it the wrong way first.
For suffering through many package development errors, I'd like to thank all the CRAN maintainers, especially Brian Ripley, Uwe Ligges and Kurt Hornik.

This book was [written and revised in the open](https://github.com/hadley/r-pkgs/) and it is truly a community effort: many people read drafts, fix typos, suggest improvements, and contribute content.
Without those contributors, the book wouldn't be nearly as good as it is, and we are deeply grateful for their help.

A special thanks goes to Peter Li, who read the book from cover-to-cover and provided many fixes.
I also deeply appreciate the time the reviewers ([Duncan Murdoch](http://www.stats.uwo.ca/faculty/murdoch/), [Karthik Ram](http://karthik.io), [Vitalie Spinu](http://vitalie.spinu.info) and [Ramnath Vaidyanathan](https://ramnathv.github.io)) spent reading the book and giving me thorough feedback.

```{r, results = "asis", echo = FALSE, eval = TRUE}
# git --no-pager shortlog -ns > contribs.txt
contribs <- read.delim("data/contribs.txt", header = FALSE, 
  stringsAsFactors = FALSE)[-1, ]
names(contribs) <- c("n", "name")

contribs <- contribs[order(contribs$name), ]
contribs$uname <- ifelse(!grepl(" ", contribs$name), 
  paste0("`@", contribs$name,"`"), contribs$name)

cat("Thanks go to all contributors who submitted improvements via github (in alphabetical order): ")
cat(paste0(contribs$uname, collapse = ", "))
cat(".\n")
```

## 约定 {#intro-conventions}

在整本书中，我们用 `fun()` 指代函数，用 `var` 来指代变量和函数参数，用 `path/` 来指代路径。

较大的代码块会将输入和输出内容混合在一起。
输出内容会被注释，因此如果你有本书的电子版本，例如访问 <https://r-pkgs.org/>，则可以轻松地将示例复制并粘贴到 R 中运行。
输出注释使用 `#>` 作为行的起始符，用于区分输出注释与常规注释。

## 版权页 {#intro-colophon}

这本书是使用 [RStudio](https://www.rstudio.com/products/rstudio/) 中的 [Quarto](https://quarto.org) 编写的。[在线网站](https://r-pkgs.org)由 [Netlify](https://www.netlify.com) 托管，并使用 GitHub actions 在每次 commit 后自动更新。
完整的源码能够在 [GitHub](https://github.com/hadley/r-pkgs) 找到。

本书的该版本由在环境中构建：

```{r}
library(devtools)
library(roxygen2)
library(testthat)
devtools::session_info()
```
